Doppler Imaging Fun

### 2019-06-07 tex/ms.tex
added probably david hogg
more words

% Author list
\author[0000-0002-0296-3826]{Rodrigo Luger}
\email{rluger@flatironinstitute.org}
\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
%
\author{Megan Bedell}
\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}

% Introduction
\section*{Placeholder}
\label{sec:intro}
%
See Figure~\ref{fig:pretty_function}.
%
\begin{figure}[h!]
    \begin{centering}
    \includegraphics[width=0.5\linewidth]{figures/pretty_function.pdf}
    \oscaption{pretty_function}{%
        This is a plot of a pretty function. And at the end of this
        caption is a symbol with a link to the \emph{exact} script
        that generated it, hosted on \textsf{GitHub}.
        \label{fig:pretty_function}
    }
    \end{centering}
\end{figure}
%

This is an equation with a ``proof'' in the form of a \textsf{Jupyter} notebook:
%
\begin{proof}{euler}
    \label{eq:euler}
    e^{i\pi} + 1 = 0.
\end{proof}
%

Check out \citet{Luger2018} and stuff.

% Bibliography
\pagebreak
\bibliography{bib}

>>>>

% Author list
\author[0000-0002-0296-3826]{Rodrigo Luger}
\email{rluger@flatironinstitute.org}
\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
%
\author{Megan Bedell}
\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}
%
\author{Probably David W. Hogg}
\affil{Center~for~Computational~Astrophysics, Flatiron~Institute, New~York, NY}

%
\section{Introduction}
Check out \citet{Luger2019} and \citet{Bedell2019} and stuff.

%
\section{Uniform surfaces}
\label{sec:uniform surfaces}

Let $I(\lambda, x, y)$ be the Doppler-shifted intensity observed at wavelength $\lambda$ at
position $x, y$ on the surface of the star. We may express it as
%
\begin{align}
    \label{eq:IntensityUnif}
    I(\lambda, x, y) &= I_0\Big(\mathcal{D}^{-1}_{\beta(x, y)}(\lambda)\Big)
\end{align}
%
where $I_0$ is the (spatially uniform) spectrum in the original, unshifted frame
and 
%
\begin{align}
    \mathcal{D}^{-1}_{\beta(x, y)}(\lambda) &= \frac{\lambda}{1 + \beta(x, y)} \nonumber \\
                                            &\equiv \lambda_0
\end{align}
%
is the non-relativistic \emph{inverse} Doppler operator, which takes as input the shifted (observed)
wavelength $\lambda$ and returns the unshifted wavelength $\lambda_0$.
The quantity
%
\begin{align}
    \beta(x, y) &= \frac{v(x, y)}{c}
\end{align}
%
is the ratio of the radial velocity $v(x, y)$ at a point on the
surface to the speed of light.

If we Taylor expand Equation~(\ref{eq:IntensityUnif}) about $\beta = 0$, we obtain
%
\begin{align}
    \label{eq:TaylorUnifExplicit}
    I(\lambda, x, y) 
        &=
        I_0(\lambda_0) \Bigg|_{\beta=0}
        + 
        \frac{\mathrm{d}I_0(\lambda_0)}{\mathrm{d}\beta} \Bigg|_{\beta=0} \Delta\beta(x, y)
        + 
        \frac{\mathrm{d}^2I_0(\lambda_0)}{\mathrm{d}\beta^2} \Bigg|_{\beta=0} \Delta\beta(x, y)^2
        +
        ... 
\end{align}
%
The derivatives of the spectrum $I_0(\lambda_0)$ with respect to
$\beta$ are found by application of Fa\`a di Bruno's formula for taking high
order derivatives of the chain rule:
%
\begin{proof}{faa_di_bruno}
    \label{eq:dIdbeta}
    \frac{\mathrm{d}^n I_0(\lambda_0)}{\mathrm{d}\beta^n} \Bigg|_{\beta=0} &=
    \sum_{k=1}^n \frac{\mathrm{d}^k I(\lambda_0)}{\mathrm{d}\lambda_0^k} \lambda_0^k P_{nk}
\end{proof}
%
where
%
\begin{proof}{faa_di_bruno}
    \label{eq:Pnk}
    P_{nk} \equiv B_{n, k}\Bigg( \Big\{(-1)^j j! \Big\}_{j=1}^{n - k + 1} \Bigg)
\end{proof}
%
is an integer computed from the incomplete Bell polynomial $B_{n, k}$.
Given this result, and noting that $\lambda_0 = \lambda$ when $\beta = 0$,
we may re-write Equation~(\ref{eq:TaylorUnifExplicit}) as
%
\begin{align}
    \label{eq:TaylorUnifSum}
    I(\lambda, x, y) 
        &=
        I_0(\lambda)
        + 
        \sum_{n=1}^\infty
            \Bigg(
                \sum_{k=1}^n \frac{\mathrm{d}^k I(\lambda)}{\mathrm{d}\lambda^k} \lambda^k P_{nk} 
            \Bigg)
            \Bigg(
                \Delta\beta(x, y)^n
            \Bigg)
\end{align}
%
Assuming we only have access to spatially unresolved spectra of the star, the quantity
we observe is the integral of the intensity over the surface of the star, which we
denote $S$:
%
\begin{align}
    \label{eq:TaylorUnifSumIntegral}
    S(\lambda) 
        &=
        \pi I_0(\lambda)
        + 
        \sum_{n=1}^\infty
            \Bigg(
                \sum_{k=1}^n \frac{\mathrm{d}^k I(\lambda)}{\mathrm{d}\lambda^k} \lambda^k P_{nk} 
            \Bigg)
            \Bigg(
                \int{\Delta\beta(x, y)^n}\mathrm{d}\Omega
            \Bigg)
\end{align}
%
where $\int\mathrm{d}\Omega$ denotes the surface integral over the visible disk
of the star.

Note, importantly, that the terms in the first set of parentheses depend \emph{only} on the wavelength,
while the terms in the second set of parentheses depend \emph{only} on the position.
This Taylor expansion has therefore allowed us to deconvolve the effects of the Doppler
shift from the actual spectrum of the star.

% Bibliography
\bibliography{bib}
